Distributed multi-objective evolutionary optimization using island-based selective operator application

### 2018-06-10 hpmoon-asoco.tex
Things not addressed since first version @fergunet

The previously described four approaches have been run with two
different chromosome lengths ($L$): 512 and 2048. Different number of
islands ($P$) have also been compared: 8, 16, 32, 64 and 128. This
maximum number of islands has also been  used in a previous work in the
literature \cite{Martens13asynchronous}. The crossover and mutation
chosen, SBX and polynomial, have also been  used previously by other
authors in \cite{Durillo08masterslave,CaoZLL17}.  % SBX is first mentioned
                                % here. Has to explain - JJ

@@

The criterion used for terminating an experiment has been the running
time: 25 seconds for dimension 512 and 100s (four times more) for
2048. According to Alba and Luque \cite{EVALUATIONPARALLEL}, other stop criteria such as the number of evaluations required to attain a solution, may be misleading depending on the studied scenario. In our case we have used time instead of the number of evaluations firstly
because our hypothesis argues that the time saved in crossover and
mutation can be spent on improving the sub-populations and more
operations and migrations can be achieved. Also, we are using
different number of islands (with different sub-population sizes) and that
could lead to different execution times, so it would be difficult to
compare different times and quality of solutions at the same time. The number of generations between migrations has been set to 5, as this number is usually repeated in the literature \cite{Deb03distributed,Martens13asynchronous}. \textcolor{blue}{Migration is performed asynchronously, as it has the advantage of being a non-blocking operation \cite{TalbiUnified2018}. The individual chosen to migrate is selected from the subpopulation using Binary Tournament, as proposed in previous papers  \cite{xiong2003parallel,Xiao03specialized}. Whenever an island starts the migration step, the migrated individual is sent to another randomly selected island. This makes it possible a dissemination of the modified parts of the individuals among the whole set of islands, thus avoiding a specific synchronization step to compose solutions obtained by different islands, as occurs other works \cite{Dorronsoro13superlinear}.}
 The whole parameter set is summarized in Table \ref{tab:parameters}. 
 \textcolor{blue}{It is important to point out that we have carried out experiments modifying only the number of islands and the size of the problem, as other researchers have done \cite{CaoZLL17,Dorronsoro13superlinear,DorronsoroPSO2018,Martens13asynchronous,Durillo08masterslave}, who did not carry out studies on other parameters apart from these. This allows us to focus on the objective of this article, which is to demonstrate that on equal terms, the use of SLA can lead to improved performance depending on the combination of the number of islands and the size of the chromosome.}

>>>>

The previously described four approaches have been run with two
different chromosome lengths ($L$): 512 and 2048. Different number of
islands ($P$) have also been compared: 8, 16, 32, 64 and 128. This
maximum number of islands has also been  used in a previous work in the
literature \cite{Martens13asynchronous}. The crossover and mutation
chosen, SBX and polynomial, have also been  used previously by other
authors in \cite{Durillo08masterslave,CaoZLL17}.  % SBX is first mentioned
% here. Has to explain - JJ
% Still not done - JJ

@@

The criterion used for terminating an experiment has been the running
time: 25 seconds for dimension 512 and 100s (four times more) for
2048. According to Alba and Luque \cite{EVALUATIONPARALLEL}, other stop criteria such as the number of evaluations required to attain a solution, may be misleading depending on the studied scenario. In our case we have used time instead of the number of evaluations firstly
because our hypothesis argues that the time saved in crossover and
mutation can be spent on improving the sub-populations and more
operations and migrations can be achieved. Also, we are using
different number of islands (with different sub-population sizes) and that
could lead to different execution times, so it would be difficult to
compare different times and quality of solutions at the same time.

The number of generations between migrations has been set to 5, as
this number is usually repeated in the literature
\cite{Deb03distributed,Martens13asynchronous}. \textcolor{blue}{Migration
  is performed asynchronously, as it has the advantage of being a
  non-blocking operation \cite{TalbiUnified2018}. The individual
  chosen to migrate is selected from the subpopulation using Binary
  Tournament, as proposed in previous papers
  \cite{xiong2003parallel,Xiao03specialized}. Whenever an island
  starts the migration step, the migrated individual is sent to
  another randomly selected island. This makes it possible a
  dissemination of the modified parts of the individuals among the
  whole set of islands, thus avoiding a specific synchronization step
  to compose solutions obtained by different islands, as occurs other
  works \cite{Dorronsoro13superlinear}.} 
 The whole parameter set is summarized in Table \ref{tab:parameters}. 
 \textcolor{blue}{It is important to point out that we have carried out experiments modifying only the number of islands and the size of the problem, as other researchers have done \cite{CaoZLL17,Dorronsoro13superlinear,DorronsoroPSO2018,Martens13asynchronous,Durillo08masterslave}, who did not carry out studies on other parameters apart from these. This allows us to focus on the objective of this article, which is to demonstrate that on equal terms, the use of SLA can lead to improved performance depending on the combination of the number of islands and the size of the chromosome.}
